Flexibility of interactions depends on habitat suitability

### 2019-09-11 paper/manuscript.Rmd
Add some ideas to discussion

>>>>

* Summarise results
* We cannot completely distinguish between the effect on the environment on the niche itself or on neutral processes
* The environment can certainly influence the number of interactions but its very variable among species
* We don't know wether specialists are also constrained to interact with species they like because our dataset is biased for species that are there. This is we are only observing those specialist that survive the lack of interaction partners
* It was clear that the compositional effect on communities is very strong and is really the determining factor at large. The environment only a fraction. However we differ that the way the rest happens is not stochastic but might be driven but driven of how environment mediates eco-evolutionary processes. 
* In the absence of abundance this is as much as we can say. 
* It is remarkable we found a signal given the amount of data we had it is realy not that much for our question. It is not surprising that the slope of suitability was small for many species as we had little data. The results hold for when species had
* The interaction between slope suitability was not related to guild. Emphasizes the relevance of eco-evolutionary processes for both guilds. If other factors like for example behaviour could explain that, we would expect markedly different outcomes for plants and pollinators. 
* Implications for community assembly and network rewiring.
